CommonMind Consortium: DLPFC

### 2020-09-23 combined_analysis/diff.networks.Rmd
Update diff networks

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf combined_analysis/diff.networks_* combined_analysis/diff.networks.html
ml git pandoc udunits proj gdal geos
git pull
R

@@

rmarkdown::render("combined_analysis/diff.networks.Rmd", output_dir="/sc/arion/scratch/hoffmg01/network")

>>>>

#

cd /hpc/users/hoffmg01/work/covarr-de/
# rm -rf combined_analysis/diff.networks_cache/html/* combined_analysis/diff.networks.html
ml git pandoc udunits proj gdal geos
git pull
R

@@

rmarkdown::render("combined_analysis/diff.networks.Rmd")

ll /hpc/users/hoffmg01/work/covarr-de/combined_analysis/diff.networks_cache/html/

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf combined_analysis/diff.networks_* combined_analysis/diff.networks.html
ml git pandoc udunits proj gdal geos
git pull
cd /sc/arion/scratch/hoffmg01/network/
\cp -f /hpc/users/hoffmg01/work/covarr-de/combined_analysis/diff.networks.Rmd /sc/arion/scratch/hoffmg01/network
R

system("cd /hpc/users/hoffmg01/work/covarr-de; git pull")

rmarkdown::render("diff.networks.Rmd", output_dir="/sc/arion/scratch/hoffmg01/network/", intermediates_dir='/sc/arion/scratch/hoffmg01/network/')

ll /hpc/users/hoffmg01/work/covarr-de/combined_analysis/diff.networks_cache/html/
